Python as a machine learning language: experiences from the scikit-learn project

### 2013-05-03 paper.tex
tentative abstract

>>>>

\begin{abstract}
The scikit-learn project aims to create an open source
machine learning library for the Python programming language,
offering performant implementations of well-established learning algorithms,
and tying in with the ecosystem of scientific software
that has evolved around the NumPy and SciPy packages.
Since the start of the project in 2009,
it has gathered a sizeable user base.

This paper discusses design choices made
in both the programmers' interface (API) and the implementation
of scikit-learn.
It also highlights obstacles faced by users and implementers
of machine learning algorithms in the Python language.
\end{abstract}
